Playing Games: A Case Study in Active Learning Applied to Game Theory

### 2015-06-30 paper/paper.tex
Seaborn version of the axelrod plot.

\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true]{biblatex}
\addbibresource{library.bib}

@@

One of the weaknesses of this approach is that all participants observe the play
by all the teams. Whilst from a mathematical perspective reputation is inferred
to mean the reputation gained during a particular duel, this has the effect of
teams being able to observe how other teams seem to play. A true replication of
Axelrod's tournament would not allow for this. One possibility would invite
participants to leave the room which might be logistically constrained. From a
pedagogic point of view however, having participants observe the duels often
leads to a much more engaged discussion (after as well as during the activity).

@@

This tournament can be used to introduce further game theoretic topics with
slight modifications:

>>>>

\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=draft]{biblatex}
%\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=numeric]{biblatex}
%\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=authoryear]{biblatex}
\addbibresource{library.bib}

@@

One of the inconsistancies of this approach is that all participants observe the
play by all the teams. Whilst from a mathematical perspective reputation is
inferred to mean the reputation gained during a particular duel, this has the
effect of teams being able to observe how other teams seem to play. A true
replication of Axelrod's tournament would not allow for this. One possibility
would invite participants to leave the room which might be logistically
constrained. From a pedagogic point of view however, having participants observe
the duels often leads to a much more engaged discussion (after as well as during
the activity).

@@

This activity can be used to introduce further game theoretic topics with
slight modifications:
